    ---
    title: "Speeding up GWR like models with mgwrsar package using Target Points, rough gaussian kernel and parallelisation"
    author: "Ghislain Geniaux"
date: "`r Sys.Date()`"
    output:
      rmarkdown::html_vignette:
        keep_md: false
    vignette: >
      %\VignetteIndexEntry{Speeding up GWR like models with mgwrsar package using Target Points, rough gaussian kernel and parallelisation}
      %\VignetteEngine{knitr::rmarkdown}
      %\VignetteEncoding{UTF-8}
    ---

    ```{r setup, include=FALSE}
    target_url <- "https://ggeniaux.github.io/mgwrsar_vignettes/Speeding_up_GWR_like_models.html"
    ```

    This vignette is hosted online due to size and computational constraints.

    **Online version:** <https://ggeniaux.github.io/mgwrsar_vignettes/Speeding_up_GWR_like_models.html>

    ```{r redirect, echo=FALSE, results='asis'}
    cat(sprintf(
      '<p><strong>Online version:</strong> <a href="%s">%s</a></p>',
      target_url, target_url
    ))

    # Meta refresh (works without JS); short delay to keep the page readable
    cat(sprintf('<meta http-equiv="refresh" content="3; url=%s">', target_url))

    # JS redirect as a fallback
    cat(sprintf("<script>setTimeout(function(){ window.location.href = '%s'; }, 3000);</script>", target_url))
    ```
